%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {WordPress Developer} % Job title
    {TECHVERX} % Organization
    {Lahore, Pakistan} % Location
    {Jan. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Added custom field groups added to WordPress data like posts (including all custom post types), users and categories (including all custom taxonomies), so that it will be available in their respective \textbf{WP REST API endpoints}.}
        \item {\textbf{Customizing WordPress plugin} according to clients needs.}
        \item {Developed an Custom Posts to use as projects in dashboard which is getting content from \textbf{ACF(advanced custom field)}.To organize these post we have to have a category for which \textbf{taxonimies} were used.}
        \item {Created \textbf{Custom WordPress Themes} with the \textbf{Custom Post Types} and \textbf{ACF} as it optimize site and increase usabilty. Which \textbf{improved SEO} trmondesly.}
        \item {Managed version control with \textbf{Git} and \textbf{Github}.Used \textbf{JIRA} to manage project timeline for updates and identifying issues.}
        \item {Planned website development, converting mock ups into usable web presence with \textbf{HTML5}, \textbf{CSS3}, \textbf{jQuery} and \textbf{SASS}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Frontend/WordPress Developer} % Job title
    {UNIVERSAL SOLZ.} % Organization
    {Lahore, Pakistan} % Location
    {Aug. 2020 - Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created and updated re-usable code libraries to streamline \textbf{WordPress} development cycle.}
        \item {Designed and made \textbf{responsive} layouts to meet usability and performance requirements.}
        \item {Developed an Custom Post to use as projects in dashboard which is getting content from \textbf{ACF(advanced custom field)}.}
        \item {Created UI template for the \textbf{Custom Post Types} and \textbf{ACF}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Frontend Developer} % Job title
    {FIWD INC.} % Organization
    {Lahore, Pakistan} % Location
    {Jan. 2020 - Jul. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and made \textbf{responsive} layouts to meet usability and performance requirements.}
        \item {Converted design assets into \textbf{responsive} component-based \textbf{HTML5}, \textbf{CSS3}, \textbf{JavaScript} ,\textbf{Bootstrap}, \textbf{SASS} and \textbf{LESS}.}
        \item {Developed an layout for a project with \textbf{Tailwindcss}.}
        \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer Intern} % Job title
    {WEBSOL} % Organization
    {Lahore, Pakistan} % Location
    {Nov. 2019 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed \textbf{API server} which is communicating with client and used \textbf{Heroku} for deployment.}
        \item {Won the \textbf{2nd prize in final evaluation}.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
