%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Frontend} % Affiliation/role
    {Dryve} % Organization/group
    {{\href{https://www.getdryve.com/}{Link}}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Integrated WordPress into provided HTML, CSS and JavaScript static site. I used CPT UI to add custom post types in for new testimonials and used Elementor as to update content in the site and posting blogs.}
        \item {Added Gulp.js to compile the SASS.}
        \item {Added new changes for appealing frontend website architecture.}
        \item {For security added WordPress security plugins.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Frontend} % Affiliation/role
    {Friday(POS)} % Organization/group
    {{\href{https://www.fridaypos.com/}{Link}}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Integrated WordPress into provided HTML, CSS and JavaScript static site. I used CPT UI to add custom post types in for new testimonials and used ACF as custom fields to add functionality to update content in the site and post blogs.}
        \item {Added blog page to in which I used WPQuery to get posts by ID and used featured image as thumbnail for cards.}
        \item {Made some new changes by adding new slider for which I used \textbf{Slick Slider} in the home page.}
        \item {Added a previously made price table in the price pages.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Frontend} % Affiliation/role
    {Lawcus} % Organization/group
    {{\href{https://www.lawcus.com/}{Link}}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Developed WordPress site with Elementor page builder.Imported the available demo theme.}
        \item {Updated the content according to client's needs.}
        \item {Added \textbf{Chatbot} in the home page.}
        \item {Used \textbf{CF7(ContactForm 7)} in the contact form.}
      \end{cvitems}
    }

%---------------------------------------------------------

\cventry
    {Frontend} % Affiliation/role
    {eVisit} % Organization/group
    {{\href{https://www.evisit.com/}{Link}}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Developed WordPress site with WPBakery page builder.Imported the available demo theme.}
        \item {Updated the content according to client's needs.}
        \item {Made some new changes by adding new slider for which I used \textbf{Slick Slider} in the home page.}
        \item {Added \textbf{Google Tag Manager} to measure our advertising ROI as well as track our social networking sites.}
      \end{cvitems}
}

%---------------------------------------------------------

\cventry
    {Frontend} % Affiliation/role
    {LightPoint} % Organization/group
    {{\href{https://www.lightpointft.com/}{Link}}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Developed WordPress site with Elementor page builder.}
        \item {Updated the content according to client's needs.}
        \item {Improved LCP and FCP by optimizing image sizes.}
      \end{cvitems}
    }
%---------------------------------------------------------

\cventry
    {Frontend} % Affiliation/role
    {Techverx} % Organization/group
    {{\href{https://www.techverx.com/}{Link}}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Developed WordPress site with Bold page builder.}
        \item {Updated the content according to marketing manager's needs.}
        \item {Improved LCP and FCP by optimizing image sizes.}
      \end{cvitems}
    }
%---------------------------------------------------------

\cventry
    {} % Affiliation/role
    {Honorable Mentions} % Organization/group
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {\textbf{\color{red}{\href{https://www.vpix360.com/}{VPIX}}}}
        \item {\textbf{\color{red}{\href{https://www.postalmethods.com/}{Postal Methods}}}}
        \item {\textbf{\color{red}{\href{https://www.hamararishta.pk/}{Hamara Rishta}}}}
        \item {\textbf{\color{red}{\href{https://www.akautocenter.ae/}{AK Auto Center}}}}
        \item {\textbf{\color{red}{\href{https://www.codingibex.com/}{Coding Ibex}}}}
        \item {\textbf{\color{red}{\href{https://www.shamsaali.com/}{Shamsa Ali (Member of Parliment)}}}}
        \item {\textbf{\color{red}{\href{https://www.buneyad.com/}{Buneyad}}}}
        \item {\textbf{\color{red}{\href{https://www.lhdcarshowroom.co.uk/}{The Left Hand Drive Car Showroom}}}}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

